Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-05 ex2/paper/paper.tex
Added pruning plots

>>>>

% AH This figures currently serve as placeholder/example. TOOD: decide what to plot exactly
\begin{figure}[t]
\includegraphics[width=\columnwidth]{../prune_CAIA_backdoor_15/prune.pdf}
\caption{Performance metrics throughout the pruning process.}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../prune_CAIA_backdoor_17/{prune_1.00_nn_0_bd}.pdf}
\caption{Correlation coefficient of neuron activation with backdoor usage throughout the pruning process.}
\end{figure}
